### 2014-03-04 Studies/Chicago_2012/Report/Chicago_Fire.tex
Chicago Fire: add smv image, update results, input files, and processing script

>>>>

In Fig.~(\ref{fig:hrr}), the solid line is the FDS HRR from the venting conditions that represent our attempt to model the on-scene conditions. The dashed line represents the case where the rear door opening and subsequent beta side breach do not occur. The dash-dotted line is the prescribed FDS input HRR. We can see that within the first 10 seconds, there are under-ventilated conditions within the structure as the modeled HRR is below the prescribed HRR. The HRR first peaks at just under 9 MW at approximately 20 seconds into the simulation. The HRR proceeds to drop to 5 MW as the available oxygen inside the structure gets consumed. There is insufficient available oxygen in the structure to combust all of the fuel. As a result there is excess fuel buildup within the attic and back porch and burning occurs exterior to the structure where fuel at oxygen can mix at the various vents. Fig.~(\ref{fig:smv_ext_fire}) illustrates flaming combustion through the failed Charlie side window and attic breach just after the second fire ignites at 40s. The HRR spikes back up to 9 MW at 58 seconds (after additional wall breaches, see Table~\ref{tab:vents}) before again dropping to 5 MW.

\begin{figure}[h!]
\centering
\includegraphics[width=.80\textwidth]{../Figures/smv_exterior_fire}
\caption{Smokeview rendering showing combustion occurring exterior to the structure on the Charlie side.}
\label{fig:smv_ext_fire}
\end{figure}
